Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-11-10 paper/submit/referee-response.txt

We thank the referee for the constructive report and suggested improvements. To
address the referee's concerns, we have redone and rewritten our population
modeling to provide a probabilistic classification of each pair as being
"comoving" or "field." Though our conclusions or results haven't changed as a
result of this change, we agree that it is more robust and more honest to
provide probabilities for each pair rather than perform a hard cut on likelihood
ratio increase. We believe that the re-analysis and re-write of our modeling
section will address many of the broader concerns the referee had with this work
and thus don't reply to every issue specifically. We've also moved away from
using the word "confirmed comoving pairs" and instead say "high-probability."
See especially sections 3 and 4 in the revised draft.

To assist the referee in interpreting the differences, we have also uploaded a
"diff"ed and rendered version of the paper that shows the changes made
(diff.pdf).

Below we address additional, specific concerns raised in the report: lines that
contain questions or comments raised by the referee begin with ">" and our
responses are listed immediately below.

> Minor concerns:
> ===============

> (1) The comparison with LAMOST metallicity and Delta-RV seems important enough
> for the case that it should probably be detailed in its own subsection, rather
> than being placed in the discussion.

We agree, and have moved it into the "Results" section - see Section 4.4

> (2) The description of the data reduction in the appendices is perhaps
> too detailed and too general, especially the 1D spectrum extraction
> and wavelength calibration. If this is standard procedure for
> MDM-MODSPEC reduction, then these details make the paper
> unnecessarily long. Publishing these details might however be useful
> if this is a novel reduction procedure - but this does not seem to be
> the case. The RV measurements on the other hand might be worth
> detailing if the procedure is truly novel, or if it is critical in
> demonstrating the level of RV precision needed for the study.

We aren't aware of a spectroscopic reduction pipeline that uses Gaussian
processes or flexible model for the spectral extraction or wavelength
calibration, so we have chosen to leave the description in this paper. We placed
it in the appendix because we agree that, while cumbersome, does describe a
novel reduction procedure. Most readers can just ignore the appendix.

> Other suggested changes:
> ========================

> Section 1, paragraph 5:
> -----------------------
> "is found to be alpha~1.5-2 out to..." Since the alpha power law is determined
> for the distribution of separations, the sentence should be reversed here: "is
> found to be alpha~1.5-2 out to projected separations ~0.65pc (~0.25degrees of
> angular separation on the sky at a distance of 150pc),"

Fixed.

> Section 1, paragraph 7:
> -----------------------
> "that falls of until" -> "that falls off until"

Fixed.

> Section 2.1, paragraph 2:
> -------------------------
> "...likelihood ratio for all stars within 10pc and with a
> difference..."
>
> Perhaps you mean:
>
> "...likelihood ratio for a star to have another star within 10 pc of
> itself, and with a difference..."

For each star in TGAS, we compute the likelihood ratio for all nearby stars
(within 10pc). We've restructured this sentence to try to clarify.

> Section 2.1, paragraph 3:
> -------------------------
> "...exclusive star pairs within 200 pc in Heliocentric distance."
> ->
> "...exclusive stars pairs with heliocentric distances d<200pc.

Fixed.

> "...used above and given the limitations of the TGAS catalog itself..."
> ->
> "...used above, and within the limits of the TGAS catalog itself
> (e.g. magnitude range), TGAS is..."

Fixed.

> "...with airmass sec z < 1.5..."
> ->
> [The airmass is an incidental parameter of the observations, not an
> intrinsic property of the targets. This statement should therefore be
> moved to section 2.2.]

Fixed.

> "...all TGAS stars within 200 pc."
> ->
> [Please cite the actual number of TGAS stars within 200pc.]

Fixed. In fact, we fixed this to read "all 195,294 TGAS stars with 2MASS
photometry within 200 pc...".

### 2017-12-07 paper/comoving-followup.tex
remove comments
edits for ref report 2

@@

\begin{abstract}
% Context
Members of widely-separated stellar binaries ($\gtrsim 0.1$~pc) or loosely bound
stellar associations and clusters are born with small spreads in kinematics and
chemistry, but are thought to physically dissociate over short timescales.
The kinematic properties of comoving stars---bound, wide or unbound but coeval
systems---are therefore sensitive to both the smooth tidal field and the
spectrum of massive perturbers (e.g., stellar remnants, dark matter, giant
molecular clouds) in the Milky Way.
% Aims
% Thus far, a few hundred confirmed comoving pairs with separations as large as
% $8~\pc$ have been discovered in the solar neighborhood using
% \project{Hipparcos} astrometry combined with radial velocity surveys.
In previous work, we identified $>4,000$ candidate comoving star pairs using
only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS) catalog
and found a large number of candidate comoving pairs with separations $\gtrsim
1~\pc$.
Without radial velocity measurements for the vast majority of these pairs, the
false-positive rate at large separations is significant ($\sim 60\%$).
% Methods
Here we present results from our own low-resolution radial-velocity survey of a
random sample of the candidate pairs to identify high-probability comoving star
pairs.
% Results
Of the \npairsobs\ observed comoving pairs, \nhighprob\ comoving pairs have
probabilities $50\%$ with separations as large as $\approx 10~\pc$, our original
search limit.
Between separations of $10^{-3}~\pc$ to $\approx 0.5~\pc$,
the number of high-probability pairs per separation decreases with increasing
separation.
From $\approx 0.5~\pc$ to $10~\pc$, the number per separation is approximately
uniform.
% Conclusions
We thus confirm the discovery of a population of comoving star pairs at very
large separations, suggesting that disrupted wide binaries and stellar
associations remain approximately spatially coherent.
% \todo{something about stellar models and chemical tagging?}
\end{abstract}

@@

Of the 323 observed star pairs, 12 have at least one member with an unreliable
(flagged) radial velocity measurement from the spectroscopic reduction pipeline.
For the remaining \npairsobs\ pairs, we construct a statistical model to
determine the probability that a given candidate comoving pair is comoving in 3D
velocity given the radial velocity and uncertainty measured in this work
combined with \tgas\ astrometric data.
For this inference, the data are the proper motions in the ICRS reference frame,
$\bs{\mu} = (\mu_{\alpha^*}, \mu_\delta)$,\footnote{$\mu_{\alpha^*} = \mu_\alpha
\, \cos\delta$} and parallax, $\varpi$, (from the
\tgas\ catalog) and barycentric radial velocity, $v_r$, for each star in a
candidate comoving pair; we assume that the sky position for each star $(\alpha,
\delta)$ is known perfectly.
For brevity in the expressions below, we define $\bs{\eta} = (\mu_{\alpha^*},
\mu_\delta, v_r)$, where, e.g., $\bs{\eta}_1$ refers to the proper motion and
radial velocity data for star 1 in the pair.
To simplify some expressions, we additionally ignore any correlations between
the observed parallax and the proper motion components (but keep the covariance
between the two proper motion components).

Our model is expressed in terms of the magnitude of the true (latent) 3D
velocity difference for each pair, $\psi = \left| \bs{v}_1 - \bs{v}_2 \right|$,
and the (global) fraction of pairs that are comoving, $f$.
For the distribution of true 3D velocity difference magnitudes, $p(\psi \given
f)$, we use a mixture model with two components
\begin{eqnarray}
    p(\psi \given f) &=& f\,p_{\rm co}(\psi) + (1-f)\,p_{\rm field}(\psi)
    \label{eq:mixture}
\end{eqnarray}
where $p_{\rm co}$ is the probability distribution function (pdf) of true
comoving pairs, and $p_{\rm field}$ is the pdf of randomly paired field stars.
Using a mixture model and inferring the mixture weight is a trick to avoid
explicitly having to sample over the probabilities for each individual object
(candidate comoving pair): this expression (\eqname~\ref{eq:mixture}) is
equivalent to the marginal likelihood under a model in which every candidate
comoving pair has an additional latent parameter (a binary flag, $q_n$) that
specifies which mixture component it belongs to
(\citealt{Hogg:2010,Foreman-Mackey:2014}).
We later use this fact to compute the probability that each pair is truly
comoving, or, more precisely, belongs to the mixture component $p_{\rm co}$.

@@

We use the model described in \sectionname~\ref{sec:pair-probs} to constrain the
fraction of stars consistent with being comoving given 3D velocities for the
candidate comoving pairs (a) with radial velocities obtained and described in
this work---\npairsobs\ pairs, and (b) with radial velocities previously
measured and released in \DR{5} of the \acronym{RAVE} survey
(\citealt{Kunder:2017})---202 pairs.
Using the posterior samples in $f$, we compute the probability (under this
model) that each given pair is comoving including the radial velocity
measurements.
\figurename~\ref{fig:f-samples} shows histograms of posterior pdf samples in $f$
for pairs with our radial velocity measurements (blue, darker histogram) and
with \acronym{RAVE} radial velocities (orange, lighter histogram); in either
case, $f \approx 40\%$ implying a contamination rate $1-f \approx 60\%$.

@@

\figurename~\ref{fig:separation} shows histograms of the tangential separation
for all pairs with radial velocities from this work and the \acronym{RAVE}
survey, with each pair weighted by the probability that it is comoving.
Interestingly, the separation distribution appears to be uniform with increasing
separation above $\approx1~\pc$.
This suggests the existence of a population of unbound wide binaries or
dissolved open clusters, which maintain approximate spatial coherence for long
times because of the small relative velocities at the time of disruption of the
constituent stars (e.g., \citealt{Jiang:2010}).
The kinematic properties of these unbound binaries and associations contain
information about the tidal field and fluctuations in the mass distribution of
the Milky Way.
With \gaia\ \DR{2}, we will be able to study the statistical properties of these
widely-separated but comoving stars at even larger separations ($>10~\pc$).
However, high resolution spectroscopy is needed to determine precise stellar
parameters, ages, and high-precision radial velocities for all of our
high-probability comoving pairs to further validate the sample.

@@

\subsection{An additional test of comoving pairs with \acronym{LAMOST}}

@@

The results presented in this work demonstrate that even at separations larger
than a parsec, a substantial fraction of candidate comoving pairs selected from
astrometry alone are consistent with being comoving given three-dimensional
velocity information.
This is exciting because it confirms the existence of what is likely a
population of nearly-coherent but unbound coeval stars.
It is also encouraging for the prospect of selecting large samples of comoving
pairs purely with astrometric data from future data releases of the \gaia\
mission (radial velocity measurements will only be released for bright stars, $G
< 12$).
However, in this work, we do not claim to report the true number or density of
large-separation comoving pairs.
To model the abundance and formation of comoving pairs, it will be crucial to
select larger samples of pairs without hard cuts on separation, tangential
velocity, signal-to-noise, or likelihood ratio, as were done with the input
sample used in this work.
It will also be important to quantify the contamination rate of (3D) comoving
pair lookalikes, especially at large separations.
However, we reiterate that given the velocity dispersions in the Galactic disk,
it is unlikely to get 3D velocity differences $<10~\kms$ (see, e.g.,
\figurename~\ref{fig:mixture-model-demo}).

Going forward, definitive confirmation of comoving star pairs may require
precise measurements of chemical abundances combined with precise radial
velocities, as demonstrated with the \acronym{LAMOST} data.
However, we would also like to \emph{test} assumptions about chemical
homogeneity, rather than simply assuming that all true comoving pairs must have
identical abundances.
For example, the outcomes of planet formation may lead to large or appreciable
abundance differences between coeval stars (e.g.,
\citealt{Pinsonneault:2001,Oh:2017a}).
We therefore caution that---to study the chemical properties of comoving pairs
and star formation in general---the comoving pairs should be selected from their
kinematics alone.

@@

The information contained in a large sample of widely-separated, comoving star
pairs spans from the dynamics of stars and dark matter in the Galaxy, the
fundamentals of star formation, and the stability of planetary systems.
Through our own low-resolution spectroscopic follow-up and a cross-match with
the RAVE \DR{5} catalog, we have identified \ncomovingtotal\ comoving star pairs
by combining these radial velocity measurements with astrometry from the \tgas\
catalog.
From a cross-match to the \acronym{LAMOST} survey, we find that candidate
comoving star pairs with small differences in radial velocities also have small
differences in iron abundance, even at large separations ($>1~\pc$).
The separation distribution of the spectroscopically-confirmed comoving star
pairs presented shows an abundance of comoving pairs at separations between
$1$--$10~\pc$ (\figurename~\ref{fig:separation-scatter}), the imposed limit in
our initial search (\citealt{Oh:2017}).
This result is further evidence (see also \citealt{Shaya:2011}) for the
existence of a population of unbound comoving stars that represent the ultimate
fate of wide binaries and moving groups that slowly dissociate due to weak
perturbations from stars (\citealt{Jiang:2010}) and other massive perturbers in
the Galaxy.
From this work it appears that modeling the population of wide binaries or
comoving stars with a monotonically decreasing separation distribution---as is
commonly done---too simple to also represent the population of unbound systems.
With future data releases from the \gaia\ mission combined with large
spectroscopic surveys, the anticipated catalogs of high-probability comoving
star pairs will offer a new ``stereo'' view on the evolution and state of our
Galaxy.

@@

@@

% \section{Old section on FMLs}
% We compute two fully marginalized likelihoods (FMLs) for the data: (1) assuming
% that the two stars are comoving with identical 3D velocity vectors (within some
% allowed small dispersion), and (2) assuming that the two stars have independent
% 3D velocity vectors drawn from a prior velocity distribution.
% We set the small allowed dispersion ($s$, in previous work) to $1~\kms$, and use
% a mixture of three Gaussian velocity components for the prior, meant to
% represent the thin disk, thick disk, and halo velocity distributions relative to
% the sun (see \citealt{Oh:2017}).

% To compute the new likelihood ratio, we modify the expressions from
% \citet{Oh:2017} to include the radial velocity measurements.
% In the same notation, this requires the following changes:
% \begin{itemize}
%   \item The projection matrix, $\mat{M}$, now has to include the radial unit
%     vector
%     \begin{equation}
%       \mat{M} =
%         \left(
%           \begin{array}{c c c}
%             -\sin\alpha & \cos\alpha & 0 \\
%             -\sin\delta \, \cos\alpha & -\sin\delta \, \sin\alpha & \cos\delta\\
%             \cos\delta \, \cos\alpha & \cos\delta \, \sin\alpha & \sin\delta
%           \end{array}
%         \right)
%     \end{equation}
%     where $(\alpha, \delta)$ are the ICRS coordinates (right ascension and
%     declination) of a given star.
%   \item The data-space velocity vector, $\vec{y}$, for one star now becomes
%     \begin{equation}
%       \vec{y} =
%         \transpose{\left(
%           \begin{array}{c c c}
%             r_i\,\mu_{\alpha}^* &
%             r_i\,\mu_{\delta} &
%             v_{r}
%           \end{array}
%         \right)}
%     \end{equation}
%     where $\mu_\alpha^*$ is the proper motion in right ascension (including the
%     $\cos{\delta}$ term), $\mu_\delta$ is the proper motion in declination, and
%     $v_r$ is the radial velocity.
%   \item The covariance matrix becomes the block-diagonal matrix
%     \begin{equation}
%       \mat{\Sigma} = \left(
%         \begin{array}{c c}
%           r^2 \, \mat{C} & 0 \\
%           0 & \sigma_{v_r}^2
%         \end{array}
%       \right)
%     \end{equation}
%     where $r$ is the distance, $\mat{C}$ is the proper motion covariance matrix
%     (from the \tgas\ catalog), and $\sigma_{v_r}$ is the radial velocity
%     uncertainty.
% \end{itemize}
% To compute the FML for hypothesis 1 for a pair of stars $(i,j)$, the data-space
% vector must become the 6-vector
% \begin{equation}
%   \vec{y} = \transpose{\left(
%     \begin{array}{c c}
%       \vec{y}_i &
%       \vec{y}_j
%     \end{array}
%     \right)}
% \end{equation}
% and the covariance matrix becomes the block-diagonal matrix
% \begin{equation}
%   \mat{\Sigma} = \left(
%     \begin{array}{c c}
%       \mat{\Sigma}_i & 0 \\
%       0 & \mat{\Sigma}_j
%     \end{array}
%   \right) \quad .
% \end{equation}

% \begin{figure}[htbp]
%   \begin{center}
%     \includegraphics[width=0.5\linewidth]{llr-vs-dv.pdf}
%   \end{center}
%   \caption{%
%     Point estimate of the 3D velocity difference between two stars in a comoving
%     pair, $|\bs{v}_1 - \bs{v}_2|$, plotted against the change in
%     log-likelihood-ratio computed when including radial velocity data.
%     Error bars are shown for a few randomly-chosen, representative pairs and
%     represent the 15th and 85th percentiles of velocity differences computed
%     from samples from the error distributions of parallax, proper motion
%     components, and radial velocity.
%     The likelihood ratio increases (i.e. the belief that the stars are comoving
%     becomes stronger) when the 3D velocity difference is small.
%     \label{fig:llr}}
% \end{figure}

% If the new likelihood ratio is larger than that computed from astrometry alone,
% the added radial velocity information supports the belief that the two stars are
% truly comoving in 3-space.
% Conversely, if the new likelihood ratio is smaller, the radial velocity data
% indicate that the pair is likely a false-positive and are not truly comoving.
% In practice, we compute the logarithm of the likelihood ratios,
% $\mathcal{R} = \ln \mathcal{L}_1/\mathcal{L}_2$; we refer to the
% proper-motion-only log-FML-ratio for a given pair of stars as
% \llrold\ (as computed in \citealt{Oh:2017}) and the log-FML-ratio including the
% radial velocity data as \llrnew.
% We consider a pair as being genuinely comoving if $\llrnew > \llrold$:
% \ncomoving\ of the \npairsobs\ comoving pairs satisfy this constraint.
% \figurename~\ref{fig:llr} shows the magnitude of the 3D velocity difference
% plotted against the change in log-likelihood-ratio, $\llrnew - \llrold$, for all
% observed pairs.
% In detail, for visualization, we sample from the error distributions over proper
% motion, parallax, and radial velocity for each star individually and compute the
% magnitude of the 3D velocity differences, $|\bs{v}_1-\bs{v}_2|$, for $2^{16}$
% samples.
% We plot the median of the resulting distribution of velocity-differences as
% dark markers (circles).
% The error bars show the 15th and 85th percentiles of the distributions for a few
% randomly chosen pairs.
% Note that pairs with large 3D velocity differences have large (negative) changes
% to their log-likelihood-ratio values.
% Some pairs with large velocity differences also have small (near zero) changes
% to the log-likelihood ratio: these are pairs where each member has a velocity
% that is an outlier with respect to the prior velocity distribution.

% The inferred 3D velocity differences and values for \llrnew\ and \llrold\ for
% all observed candidate comoving pairs are provided with the associated table
% (\tablename~\ref{tbl:data-pairs}; see Appendix~\ref{sec:table}).

% \begin{figure}[htb]
%   \begin{center}
%     \includegraphics[width=0.9\linewidth]{dx-dv.pdf}
%   \end{center}
%   \caption{%
%     Point estimate of the 3D velocity difference between two stars in a comoving
%     pair, $|\bs{v}_1 - \bs{v}_2|$, plotted against a point estimate of the 3D
%     spatial separation of the two stars, $|\bs{x}_1 - \bs{x}_2|$.
%     The distances used in the point estimates are computed using a
%     Lutz-Kelker-corrected parallax value (\citealt{Lutz:1973}).
%     \label{fig:dx-dv}}
% \end{figure}

>>>>

\newcommand{\edits}[1]{{\bf #1}}

@@

\begin{abstract}
% Context
Members of widely-separated stellar binaries ($\gtrsim 0.1$~pc) or loosely bound
stellar associations and clusters are born with small spreads in kinematics and
chemistry, but are thought to physically dissociate over short timescales.
The kinematic properties of comoving stars---bound, wide or unbound-but-coeval
systems---are therefore sensitive to both the smooth tidal field and the
spectrum of massive perturbers (e.g., stellar remnants, dark matter, giant
molecular clouds) in the Milky Way.
% Aims
% Thus far, a few hundred confirmed comoving pairs with separations as large as
% $8~\pc$ have been discovered in the solar neighborhood using
% \project{Hipparcos} astrometry combined with radial velocity surveys.
In previous work, we identified $>4,000$ candidate comoving star pairs using
only astrometric data from the Tycho-Gaia Astrometric Solution (TGAS) catalog
and found a large number of candidate comoving pairs with separations $\gtrsim
1~\pc$.
Without radial velocity measurements for the majority of these pairs, the
false-positive rate at large separations is significant ($\sim 60\%$).
% Methods
Here we present results from our own low-resolution radial-velocity survey of a
random sample of the candidate pairs to identify high-probability comoving star
pairs.
% Results
\edits{Of an initial sample of \npairsobs\ possible comoving pairs targeted
for follow-up spectroscopy, \nhighprob\ have probabilities $50\%$ with
separations as large as $\approx 10~\pc$, our original search limit.}
Between separations of $10^{-3}~\pc$ to $\approx 0.5~\pc$,
the number of high-probability pairs per separation \edits{unit} decreases with
increasing separation.
\edits{On the other hand, from $\approx 0.5~\pc$ to $10~\pc$, the number per
separation unit is approximately uniform.}
% Conclusions
\edits{This supports the existence of a population of comoving star pairs at
very large separations, suggestive of the expected population of disrupted wide
binaries and stellar associations.}

\end{abstract}

@@

Of the 323 observed star pairs, 12 have at least one member with an unreliable
(flagged) radial velocity measurement from the spectroscopic reduction pipeline.
For the remaining \npairsobs\ pairs, we construct a statistical model to
determine the probability that a given candidate comoving pair is comoving in 3D
\edits{velocity space} given the radial velocity and uncertainty measured in
this work combined with \tgas\ astrometric data.
For this inference, the data are the proper motions in the ICRS reference frame,
$\bs{\mu} = (\mu_{\alpha^*}, \mu_\delta)$,\footnote{$\mu_{\alpha^*} = \mu_\alpha
\, \cos\delta$} and parallax, $\varpi$, (from the
\tgas\ catalog) and barycentric radial velocity, $v_r$, for each star in a
candidate comoving pair; we assume that the sky position for each star $(\alpha,
\delta)$ is known perfectly.
For brevity in the expressions below, we define $\bs{\eta} = (\mu_{\alpha^*},
\mu_\delta, v_r)$, where, e.g., $\bs{\eta}_1$ refers to the proper motion and
radial velocity data for star 1 in the pair.
To simplify some expressions, we additionally ignore any correlations between
the observed parallax and the proper motion components (but keep the covariance
between the two proper motion components).

Our model is expressed in terms of the magnitude of the true (latent) 3D
velocity difference for each pair, $\psi = \left| \bs{v}_1 - \bs{v}_2 \right|$,
and the (global) fraction of pairs that are comoving, $f$.
\edits{We note that $f$ is \emph{not} the fraction of pairs that are coeval and
comoving; here we only model the fraction of pairs that are consistent with
being comoving in 3D velocity space given our measurements, some of which could
be chance alignments of stars in full-space position and velocity.
Therefore, $f$ is not a measure of our contamination rate due to random
alignments of comoving stars.}

For the distribution of true 3D velocity difference magnitudes, $p(\psi \given
f)$, we use a mixture model with two components
\begin{eqnarray}
    p(\psi \given f) &=& f\,p_{\rm co}(\psi) + (1-f)\,p_{\rm field}(\psi)
    \label{eq:mixture}
\end{eqnarray}
where $p_{\rm co}$ is the probability distribution function (pdf) of true
comoving pairs, and $p_{\rm field}$ is the pdf of randomly paired field stars.
Using a mixture model and inferring the mixture weight is a trick to avoid
explicitly having to sample over the probabilities for each individual object
(candidate comoving pair): this expression (\eqname~\ref{eq:mixture}) is
equivalent to the marginal likelihood under a model in which every candidate
comoving pair has an additional latent parameter (a binary flag, $q_n$) that
specifies which mixture component it belongs to
(\citealt{Hogg:2010,Foreman-Mackey:2014}).
We later use this fact to compute the probability that each pair is truly
comoving, or, more precisely, belongs to the mixture component $p_{\rm co}$.

@@

We use the model described in \sectionname~\ref{sec:pair-probs} to constrain the
fraction of stars consistent with being comoving given 3D velocities for the
candidate comoving pairs (a) with radial velocities obtained and described in
this work---\npairsobs\ pairs, and (b) with radial velocities previously
measured and released in \DR{5} of the \acronym{RAVE} survey
(\citealt{Kunder:2017})---202 pairs.
Using the posterior samples in $f$, we compute the probability (under this
model) that each given pair is comoving including the radial velocity
measurements.
\edits{We again note that $f$ is not a measure of contamination from chance
field star pairings, but rather just quantifies the fraction of pairs within our
observed sample that are consistent with having a small 3D velocity difference.}
\figurename~\ref{fig:f-samples} shows histograms of posterior pdf samples in $f$
for pairs with our radial velocity measurements (blue, darker histogram) and
with \acronym{RAVE} radial velocities (orange, lighter histogram); in either
case, $f \approx 40\%$ \edits{implying that $1-f \approx 60\%$ of the observed
pairs are not consistent with being comoving in 3D space.}

@@

\figurename~\ref{fig:separation} shows histograms of the tangential separation
for all pairs with radial velocities from this work and the \acronym{RAVE}
survey, with each pair weighted by the probability that it is comoving.
Interestingly, the separation distribution appears to be uniform with increasing
separation above $\approx1~\pc$.
This suggests the existence of a population of unbound wide binaries or
dissolved open clusters, which maintain approximate spatial coherence for long
times because of the small relative velocities at the time of disruption of the
constituent stars (e.g., \citealt{Jiang:2010}).
The kinematic properties of these unbound binaries and associations contain
information about the tidal field and fluctuations in the mass distribution of
the Milky Way.
With \gaia\ \DR{2}, we will be able to study the statistical properties of
widely-separated but comoving stars at even larger separations ($>10~\pc$).
\edits{However, we note that without chemical information, we don't know the
contamination rate of chance field star pairings at large separations.
High resolution spectroscopy is needed to determine precise stellar parameters,
ages, and radial velocities for all of our high-probability comoving pairs to
further validate the sample.}

@@

\subsection{An additional test of comoving pairs with \acronym{LAMOST}}
\label{sec:lamost}

@@

The results presented in this work demonstrate that even at separations larger
than a parsec, a substantial fraction of candidate comoving pairs selected from
astrometry alone are consistent with being comoving given three-dimensional
velocity information.
This is exciting because it \edits{suggests} the existence of what \edits{could
be} the population of nearly-coherent but unbound coeval stars.
It is also encouraging for the prospect of selecting large samples of comoving
pairs purely with astrometric data from future data releases of the \gaia\
mission (radial velocity measurements will only be released for bright stars, $G
< 12$).
However, in this work, we do not claim to report the true number or density of
large-separation comoving pairs.
To model the abundance and formation of comoving pairs, it will be crucial to
select larger samples of pairs without hard cuts on separation, tangential
velocity, signal-to-noise, or likelihood ratio, as were done with the input
sample used in this work.
It will also be important to quantify the contamination rate of (3D) comoving
pair lookalikes, especially at large separations.
However, we reiterate that given the velocity dispersions in the Galactic disk,
it is unlikely to get 3D velocity differences $<10~\kms$ (see, e.g.,
\figurename~\ref{fig:mixture-model-demo}).

Going forward, confirmation of comoving star pairs will require precise
measurements of chemical abundances combined with precise radial velocities, as
demonstrated above with the \acronym{LAMOST} data and \edits{in other recent
work that found large-separation pairs with similar chemical properties}
(\citealt{Andrews:2017b}).
However, we would also like to \emph{test} assumptions about chemical
homogeneity, rather than simply assuming that all true comoving pairs must have
identical abundances.
For example, the outcomes of planet formation may lead to large or appreciable
abundance differences between coeval stars (e.g.,
\citealt{Pinsonneault:2001,Oh:2017a}).
We therefore caution that---to study the chemical properties of comoving pairs
and star formation in general---the comoving pairs should be selected from their
kinematics alone.

@@

The information contained in a large sample of widely-separated, comoving star
pairs spans from the dynamics of stars and dark matter in the Galaxy, the
fundamentals of star formation, and the stability of planetary systems.
Through our own low-resolution spectroscopic follow-up and a cross-match with
the RAVE \DR{5} catalog, we have identified \ncomovingtotal\ comoving star pairs
by combining these radial velocity measurements with astrometry from the \tgas\
catalog.
From a cross-match to the \acronym{LAMOST} survey, we find that candidate
comoving star pairs with small differences in radial velocities also have small
differences in iron abundance, even at large separations ($>1~\pc$).
The separation distribution of the spectroscopically-confirmed comoving star
pairs presented shows an abundance of comoving pairs at separations between
$1$--$10~\pc$ (\figurename~\ref{fig:separation-scatter}), the imposed limit in
our initial search (\citealt{Oh:2017}).
\edits{Though there is likely contamination even in the sample of 3D comoving
star pairs identified in this work, the fact that other large-separation
($>1~{\rm pc}$, comoving star pairs in \acronym{LAMOST} and the \acronym{GALAH}
surveys (Simpson, et al., in prep.) have similar chemical properties suggests
that some fraction are real.}
This result is further evidence (see also \citealt{Shaya:2011}) for the
existence of a population of unbound comoving stars that represent the ultimate
fate of wide binaries and moving groups that slowly dissociate due to weak
perturbations from stars (\citealt{Jiang:2010}) and other massive perturbers in
the Galaxy.
\edits{We feel that this work justifies a concerted effort to obtain
high-resolution spectroscopic follow-up to use chemical information to identify
the largest-separation comoving pairs.}
From this work it appears that modeling the population of wide binaries or
comoving stars with a monotonically decreasing separation distribution---as is
commonly done---may be too simple to also represent the population of unbound
systems.
With future data releases from the \gaia\ mission combined with large
spectroscopic surveys, the anticipated catalogs of high-probability comoving
star pairs will offer a new ``stereo'' view on the evolution and state of our
Galaxy.

@@

\edits{We thank the anonymous referee for feedback that has improved the quality
of this article.}

@@
